### 2021-05-24 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Final revision - chpt 5 open questions

\section{Open Questions}
There remain two aspects of the off-chain design, which could not be addressed in detail by this thesis. These aspects are outlined briefly in the following sections.

\subsection{Representing Counterexamples}\label{sec:counterexample}
It remains to be specified, how counterexamples are represented within the network. The interaction scheme in \figref{fig:interaction_modular} suggests, that validators publish a counterexample to the network in case of a failed assertion. For this, the validators have to obtain the randomly generated values from within the execution context of the VM. With the \texttt{failwith} instruction, the top element of the stack is exposed, allowing to return an interpretable expression from the execution context. The generated values can thus be returned as a single value, a (nested) pair or a list. To allow other validators to check the assertion with a specific set of values, a modified version of the assertion code must be available on the blockchain. Instead of generating random values, this version should take these values as input parameters. Hence, the validator could create a normal transaction invoking this code with the values returned by the \texttt{failwith} instruction and publish it to the network. The counterexample is then validated like any other transaction on the blockchain.

To implement this scheme, the compiler has to generate one more contract per assertion. In addition, the assertion contract needs to know about the address of the counterexample contract, and return the address together with the generated values in case of a failure. This requires an adjustment of the storage type of the assertion contract and changes the order of origination to:
\begin{enumerate}
\itemsep-0.5em
\item \texttt{Origination(parent)}, \texttt{Origination(counterexample)}
\item \texttt{Origination(assertion, address counterexample)}
\item \texttt{Origination(controller, address [assertion], address parent)} 
\end{enumerate}

In order to reject a transaction submitting off-chain computations in case of a published counterexample, however, the network needs to be able to relate a counterexample to the respective transaction.

>>>>

\section{Open Questions}
Two remaining aspects of the off-chain design could not be addressed in detail by this thesis. These aspects are outlined briefly in the following sections.

\subsection{Representing Counterexamples}\label{sec:counterexample}
It remains to be specified, how counterexamples are represented within the network. The interaction scheme in \figref{fig:interaction_modular} suggests, that validators publish a counterexample to the network in case of a failed assertion. For this, the validators have to obtain the randomly generated values from within the execution context of the VM. With the \texttt{failwith} instruction, the top element of the stack is exposed, allowing to return an interpretable expression from the execution context. The generated values can thus be returned as a single value, a (nested) pair or a list. To allow other validators to check the assertion with a specific set of values, a modified version of the assertion code must be available on the blockchain. Instead of generating random values, this version should take these values as input parameters. Hence, the validator could create a normal transaction invoking this code with the values returned by the \texttt{failwith} instruction and publish it to the network. The counterexample is then validated like any other transaction on the blockchain. Nodes publishing false counterexamples should be penalized in order to prevent denial of service attacks. After a counterexample has been validated, the respective transaction submitting the invalid off-chain computation should be rejected. Consequently, the transaction and counterexample need to be relatable, e.g. by using an operation hash as an ID.

To implement this scheme, the compiler has to generate one more contract per assertion. In addition, the assertion contract needs to know about the address of the counterexample contract, and return the address together with the generated values in case of a failure. This requires an adjustment of the storage type of the assertion contract and changes the order of origination to:
\begin{enumerate}
\itemsep-0.5em
\item \texttt{Origination(parent)}, \texttt{Origination(counterexample)}
\item \texttt{Origination(assertion, address counterexample)}
\item \texttt{Origination(controller, [address assertion], address parent)} 
\end{enumerate}
